---
title: "NOMESCO or NCSPfi codes english names check"
author: "Sam Padmanabhuni"
date: "06/07/2023"
output: 
  github_document:
    df_print: tibble
editor_options: 
  chunk_output_type: inline
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
rm(list = ls())
library(dplyr)
library(stringr)
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
```

# Abstract

Purpose of this is to properly check NCSPfi codes names in the Usagi and
Code_Set_Compilation_v2.xlsx files. It appears there are procedure codes
in NCSPfi that have wrong name. For example: SXA10 should have name as
`Oral muccosal sampling` rather than `Epithelial mouth biopsy`

Below steps are performed:

1.    Load the Code Set Compilation with all the codes prepared by FinnGen team. Filter out NOM and MOP code sets
1.25. Get common codes present in both NOM and MOP code sets.
1.5.  Among the common codes, check for codes having both different `name_en_source` and `name_en`. Filter them out.
1.75. Codes that have different `name_en_source` and `name_en` values will have to select only one based on priority:
      - TRANSLATOR
      - DENTAL_GRP
      - GOOGLE_REVD
      - THL
2.    Load the Usagi file and filter for codes from 1.75
3.    Check if the names of the common codes between NOM and MOP code sets within Usagi has the same name in final

## 1. Load the Code Set Compilation and filter out NOM and MOP code sets

Total number of NOM and MOP code sets is
```{r}
path_to_code_set_xlsx <- "Code_Set_Compilation_v2.xlsx"
col_types = c(
  "text","text","text","text","text","date","date"
)
fg_code_set <- readxl::read_xlsx(path_to_code_set_xlsx, col_types = col_types)
fg_code_set_nom_mop <- fg_code_set |> 
  filter(grepl('^MOP|NOM',code_set))
fg_code_set_nom_mop |> nrow()
```

## 1.25.  Filter out common codes present in both NOM and MOP code sets.


```{r}
fg_code_set_nom_mop_common <- fg_code_set_nom_mop |> 
  group_by(code) |> 
  filter(n() >= 2) |> 
  arrange(code) |> 
  # Some names have double spaces which need to be changed to single space
  mutate(name_en = str_replace_all(name_en, "\\s{2}", " "))
```

The number of common codes between NOM and MOP code sets is 
```{r}
fg_code_set_nom_mop_common |> group_by(code) |> 
  distinct(code) |> 
  nrow()
```


## 1.5. Check for different `name_en_source` and `name_en` for common codes. Filter out such codes.


```{r}
fg_code_set_nom_mop_common <- fg_code_set_nom_mop_common |> group_by(code) |>
  mutate(translator_difference = any(name_en_source != first(name_en_source)),
                                     name_difference = any(name_en != first(name_en)))
```

Number of codes with translator difference
```{r}
fg_code_set_nom_mop_common |> group_by(code) |> 
  filter(translator_difference == TRUE) |> 
  distinct(code) |> 
  nrow()
```

Number of codes with name difference
```{r}
fg_code_set_nom_mop_common |> group_by(code) |> 
  filter(name_difference == TRUE) |> 
  distinct(code) |> 
  nrow()
```

Number of codes with both translator and name difference
```{r}
fg_code_set_nom_mop_common |> group_by(code) |> 
  filter(translator_difference == TRUE & name_difference == TRUE) |> 
  distinct(code) |> 
  nrow()
```
Filter out codes
```{r}
fg_code_set_nom_mop_common_diff <- fg_code_set_nom_mop_common |> 
  group_by(code) |> 
  filter(translator_difference == TRUE & name_difference == TRUE)
fg_code_set_nom_mop_common_diff
```


## 1.75. Prioritize `name_en_source` and select only top priority
```{r}
fg_code_set_nom_mop_common_diff_final <- fg_code_set_nom_mop_common_diff |> 
  group_by(code) |> 
  mutate(priority = case_when(name_en_source == "TRANSLATOR" ~ 1,
                              name_en_source == "DENTAL_GRP" ~ 2,
                              name_en_source == "GOOGLE_REVD" ~ 3,
                              name_en_source == "THL" ~ 4)) |>
  arrange(priority) |>
  slice_head(n = 1)

fg_code_set_nom_mop_common_diff_final <- fg_code_set_nom_mop_common_diff_final |> 
  select(code, name_en, name_fi, name_en_source, valid_start_date, valid_end_date) |> 
  rename("sourceCode" = "code")
```

## 2. Load usagi file
```{r}
path_to_usagi <- "../NCSPfi.usagi.csv"
ncspfi_usagi <- readr::read_csv(path_to_usagi, show_col_types = FALSE)
ncspfi_usagi_common <- semi_join(ncspfi_usagi, fg_code_set_nom_mop_common_diff_final, by="sourceCode")
```

## 3. Check the names
```{r}
usagi_fg_common <- ncspfi_usagi_common |> merge(fg_code_set_nom_mop_common_diff_final, by= "sourceCode")

```

Number of codes with different `sourceName` from Usagi and `name_en` from code set excel file
```{r}
ncspfi_usagi_common |> merge(fg_code_set_nom_mop_common_diff_final, by= "sourceCode") |> 
  select(sourceCode, sourceName, name_en, `ADD_INFO:sourceName_fi`, name_fi) |> 
  group_by(sourceCode) |> 
  filter(sourceName != name_en) |> 
  select(sourceCode) |> 
  distinct() |> 
  nrow()
```

Number of codes with different `ADD_INFO:sourceName_fi` from Usagi and `name_fi` from code set excel file
```{r}
ncspfi_usagi_common |> merge(fg_code_set_nom_mop_common_diff_final, by= "sourceCode") |>
  select(sourceCode, sourceName, name_en, `ADD_INFO:sourceName_fi`, name_fi) |> 
  group_by(sourceCode) |> 
  filter(`ADD_INFO:sourceName_fi` != name_fi) |> 
  select(sourceCode) |> 
  distinct() |> 
  nrow()
```

Number of codes with having either `sourceName` or `ADD_INFO:sourceName_fi` from Usagi different from either `name_en` or `name_fi` from code set excel file
```{r}
ncspfi_usagi_common |> merge(fg_code_set_nom_mop_common_diff_final, by= "sourceCode") |>
  select(sourceCode, sourceName, name_en, `ADD_INFO:sourceName_fi`, name_fi) |> 
  group_by(sourceCode) |> 
  filter(sourceName != name_en | `ADD_INFO:sourceName_fi` != name_fi) |> 
  select(sourceCode) |> 
  distinct() |> 
  nrow()
```
Get the codes with different `sourceName` from Usagi and `name_en` from code set excel file
```{r}
usagi_fg_common <- ncspfi_usagi_common |> merge(fg_code_set_nom_mop_common_diff_final, by= "sourceCode") |> 
  select(sourceCode, sourceName, name_en) |> 
  group_by(sourceCode) |> 
  filter(sourceName != name_en) |> 
  select(sourceCode, name_en) |>
  distinct()
```

## 4. Replace the different codes with `sourceName` with `name_en`. Write it into Usagi file

```{r}
ncspfi_usagi_updated <- ncspfi_usagi |> 
  left_join(usagi_fg_common, by = "sourceCode") |>
  mutate(sourceName = ifelse(!is.na(name_en), name_en, sourceName)) |>
  select(-name_en)

ncspfi_usagi_updated |> readr::write_csv("../../NCSPfi/NCSPfi.usagi.csv", na = "")
```
